---
output: 
  html_document
---

```{r setup, include = F, echo = F, message = F, warning = F}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.path = 'figures/')

library(dataRetrieval)
library(rnoaa)
library(purrr)
library(tidyverse)
library(lubridate)
library(tbeptools)
library(patchwork)
library(ggbeeswarm)

source('R/funcs.R')

pth <- 'data/raw/epchc.xlsx'

chldat <- read_importwq(pth, download_latest = T)

# key for noaa data
noaa_key <- Sys.getenv("NOAA_KEY")
```

# {.tabset}

## 2020 {.tabset .tabset-pills}

```{r}
yrsel <- 2020
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2019 {.tabset .tabset-pills}

```{r}
yrsel <- 2019
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2018 {.tabset .tabset-pills}

```{r}
yrsel <- 2018
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2017 {.tabset .tabset-pills}

```{r}
yrsel <- 2017
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2016 {.tabset .tabset-pills}

```{r}
yrsel <- 2016
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2015 {.tabset .tabset-pills}

```{r}
yrsel <- 2015
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2014 {.tabset .tabset-pills}

```{r}
yrsel <- 2014
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2013 {.tabset .tabset-pills}

```{r}
yrsel <- 2013
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2012 {.tabset .tabset-pills}

```{r}
yrsel <- 2012
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2011 {.tabset .tabset-pills}

```{r}
yrsel <- 2011
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```

## 2010 {.tabset .tabset-pills}

```{r}
yrsel <- 2010
hydroests <- hydroload_est(yrsel, noaa_key)
```

### OTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('OTB', chldat, hydroests, yrsel)
```

### HB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('HB', chldat, hydroests, yrsel)
```

### MTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('MTB', chldat, hydroests, yrsel)
```

### LTB 

```{r fig.height = 7, fig.width = 8}
chlhydplo_fun('LTB', chldat, hydroests, yrsel)
```
